Latent Predicate Networks: Concept Learning with Probabilistic Context-Sensitive Grammars

### 2014-10-21 drafts/cfp/draft.tex
tweaking the tables and figures

\textbf{Example:} The following is an RCG for the 3-copy language
$\{www | w \in \{a, b\}^*\}$:
\begin{alignat*}{3}
&S(XYZ) &&\rightarrow A(X, Y, Z)\\
&A(aX, aY, aZ) &&\rightarrow A(X, Y, Z)\\
&A(bX, bY, bZ) &&\rightarrow A(X, Y, Z)\\
&A(\epsilon, \epsilon, \epsilon) &&\rightarrow 
\end{alignat*}

@@

We extend RCGs to PRCGs by annotating each clause $C_k \in P$ with
probabilities $p_k$ such that for all predicates ${A \in N, \,
  \sum_{k:head(C_k)=A} p_k = 1}$. An PRCG defines a distribution over
strings $x$ by sampling from derivations of $S(x)$ according to the
product of probabilities of clauses used in that derivation. This is a
well defined distribution as long as no probability mass is placed on
derivations of infinite length; in this paper, we only consider PRCGs
with derivations of finite length, so we need not worry about this
requirement.

@@

lpn(P-IN) :- msw(P,V), reduce(P-IN,V).
		\end{verbatim}
		\subcaption{}
		\label{fig:prism}
	\end{minipage}
	\caption{Possible encodings of the 2-copy language as (\subref{fig:grammar}) an LPN, (\subref{fig:prism}) a PRISM program.}
	\label{fig:copy}
\end{figure}

@@

\begin{table}[t]
\begin{tabular}{>{\tiny} l >{\tiny} l >{\tiny} l}
\multicolumn{3}{>{\tiny}c}{$S$(X Y) $\leftarrow$ $A_1$(X, Y) : 1.0000} \\
\multicolumn{3}{>{\tiny}c}{$A_1$(X Y, U V) $\leftarrow$ $A_2$(X, U), $A_3$(V, Y) : 0.5002} \\
\multicolumn{3}{>{\tiny}c}{$A_1$(X Y, U V) $\leftarrow$ $A_3$(Y, V), $A_4$(X, U) : 0.3428} \\
\multicolumn{3}{>{\tiny}c}{$A_1$(X Y, U V) $\leftarrow$ $A_1$(V, Y), $A_4$(X, U) : 0.0796} \\
\multicolumn{3}{>{\tiny}c}{$A_1$(X Y, U V) $\leftarrow$ $A_1$(Y, V), $A_2$(X, U) : 0.0712} \\
\multicolumn{3}{>{\tiny}c}{$A_1$(X Y, U V) $\leftarrow$ $A_2$(Y, X), $A_3$(V, U) : 0.0021} \\
\multicolumn{3}{>{\tiny}c}{$A_1$(X Y, U V) $\leftarrow$ $A_1$(V, Y), $A_2$(X, U) : 0.0013} \\
\multicolumn{3}{>{\tiny}c}{$A_1$(X Y, U V) $\leftarrow$ $A_2$(V, X), $A_3$(Y, U) : 0.0008} \\
\multicolumn{3}{>{\tiny}c}{$A_1$(X Y, U V) $\leftarrow$ $A_1$(X, U), $A_2$(V, Y) : 0.0008} \\
\multicolumn{3}{>{\tiny}c}{$A_1$(X Y, U V) $\leftarrow$ $A_1$(X, U), $A_2$(Y, V) : 0.0008} \\
\multicolumn{3}{>{\tiny}c}{$A_1$(X Y, U V) $\leftarrow$ $A_1$(X, U), $A_4$(Y, V) : 0.0004} \\
$A_2$(before, comes) : 0.73 & $A_4$(after, comes) : 1.0  &
$A_3$(one, two) : 0.40 \\
$A_3$(two, three) : 0.21 &
$A_3$(three, four) : 0.11 &
$A_3$(four, five) : 0.07 \\
$A_3$(five, six) : 0.05 &
$A_3$(six, seven) : 0.04 \\
$A_3$(eight, nine) : 0.03 &
$A_3$(seven, eight) : 0.03 \\
$A_2$(fifty, fifty) : 0.04 &
$A_2$(thirty, thirty) : 0.04 \\
$A_2$(eighty, eighty) : 0.03 &
$A_3$(null, one) : 0.02 \\
$A_2$(forty, forty) : 0.03 &
$A_2$(twenty, twenty) : 0.03 \\
$A_2$(seventy, seventy) : 0.03 &
$A_2$(sixty, sixty) : 0.03 \\
$A_2$(ninety, ninety) : 0.03 &
$A_3$(eighteen, nineteen) : 0.01 \\
$A_3$(sixteen, seventeen) : 0.0049 &
$A_3$(eleven, twelve) : 0.0044 \\
$A_3$(nine, ten) : 0.0044 &
$A_3$(thirteen, fourteen) : 0.0044 \\
$A_3$(fourteen, fifteen) : 0.0039 &
$A_3$(ten, eleven) : 0.0034 \\
$A_2$(null, fifty) : 0.0043 &
$A_3$(eighty, null) : 0.0030 \\
$A_3$(seventeen, eighteen) : 0.0030 &
$A_3$(nine, sixty) : 0.0025 \\
$A_2$(nine, seventy) : 0.0029 &
$A_3$(nine, forty) : 0.0020 \\
$A_2$(null, thirty) : 0.0022 &
$A_2$(nine, ninety) : 0.0022 \\
$A_3$(twelve, thirteen) : 0.0015 &
$A_3$(fifteen, sixteen) : 0.0015 \\
$A_3$(null, comes) : 0.0010 &
$A_2$(twenty, after) : 0.0014 \\
$A_2$(sixty, before) : 0.0007 &
$A_3$(nineteen, comes) : 0.0005 \\
$A_4$(nine, thirty) : 0.0010 & \\
\end{tabular}
\caption{The grammar which produced Table \ref{tab:results}.}
\label{tab:grammar}
\end{table}

>>>>

%% \textbf{Example:} The following is an RCG for the 3-copy language
%% $\{www | w \in \{a, b\}^*\}$:
%% \begin{alignat*}{3}
%% &S(XYZ) &&\rightarrow A(X, Y, Z)\\
%% &A(aX, aY, aZ) &&\rightarrow A(X, Y, Z)\\
%% &A(bX, bY, bZ) &&\rightarrow A(X, Y, Z)\\
%% &A(\epsilon, \epsilon, \epsilon) &&\rightarrow 
%% \end{alignat*}

@@

We extend RCGs to PRCGs by annotating each clause $C_k \in P$ with
probabilities $p_k$ such that for all predicates ${A \in N, \,
  \sum_{k:head(C_k)=A} p_k = 1}$. An PRCG defines a distribution over
strings $x$ by sampling from derivations of $S(x)$ according to the
product of probabilities of clauses used in that derivation. This is a
well defined distribution as long as no probability mass is placed on
derivations of infinite length; in this paper, we only consider PRCGs
with derivations of finite length, so we need not worry about this
requirement. See Figure \ref{fig:grammar} for an example of the context-sensitive 2-copy language $\{ww\,|w \in \{a,b\}^+\}$ as a PRCG.

@@

lpn(P-IN) :- msw(P,V), reduce(P-IN,V).
		\end{verbatim}
		\subcaption{}
		\label{fig:prism}
	\end{minipage}
	\caption{Possible encodings of the 2-copy language $\{ww\,|\, w \in \{a,b\}^+\}$ as (\subref{fig:grammar}) an LPN, (\subref{fig:prism}) a PRISM program.}
	\label{fig:copy}
\end{figure}

@@

\begin{table}[t]
\begin{tabular}{>{\tiny} l >{\tiny} l}
\multicolumn{2}{>{\tiny}c}{$S$(X Y) $\leftarrow$ $A_1$(X, Y) : 1.0000} \\
\multicolumn{2}{>{\tiny}c}{$A_1$(X Y, U V) $\leftarrow$ $A_2$(X, U), $A_3$(V, Y) : 0.5002} \\
\multicolumn{2}{>{\tiny}c}{$A_1$(X Y, U V) $\leftarrow$ $A_3$(Y, V), $A_4$(X, U) : 0.3428} \\
\multicolumn{2}{>{\tiny}c}{$A_1$(X Y, U V) $\leftarrow$ $A_1$(V, Y), $A_4$(X, U) : 0.0796} \\
\multicolumn{2}{>{\tiny}c}{$A_1$(X Y, U V) $\leftarrow$ $A_1$(Y, V), $A_2$(X, U) : 0.0712} \\
\multicolumn{2}{>{\tiny}c}{$A_1$(X Y, U V) $\leftarrow$ $A_2$(Y, X), $A_3$(V, U) : 0.0021} \\
\multicolumn{2}{>{\tiny}c}{$A_1$(X Y, U V) $\leftarrow$ $A_1$(V, Y), $A_2$(X, U) : 0.0013} \\
\multicolumn{2}{>{\tiny}c}{$A_1$(X Y, U V) $\leftarrow$ $A_2$(V, X), $A_3$(Y, U) : 0.0008} \\
\multicolumn{2}{>{\tiny}c}{$A_1$(X Y, U V) $\leftarrow$ $A_1$(X, U), $A_2$(V, Y) : 0.0008} \\
\multicolumn{2}{>{\tiny}c}{$A_1$(X Y, U V) $\leftarrow$ $A_1$(X, U), $A_2$(Y, V) : 0.0008} \\
\multicolumn{2}{>{\tiny}c}{$A_1$(X Y, U V) $\leftarrow$ $A_1$(X, U), $A_4$(Y, V) : 0.0004} \\
$A_2$(before, comes) : 0.7316 & $A_4$(after, comes) : 0.9990  \\
$A_3$(one, two) : 0.3993 &
$A_3$(two, three) : 0.2063 \\
$A_3$(three, four) : 0.1093 &
$A_3$(four, five) : 0.0734 \\
$A_3$(five, six) : 0.0502 &
$A_3$(six, seven) : 0.0355 \\
$A_3$(eight, nine) : 0.0290 &
$A_3$(seven, eight) : 0.0271 \\
$A_2$(fifty, fifty) : 0.0375 &
$A_2$(thirty, thirty) : 0.0361 \\
$A_2$(eighty, eighty) : 0.0339 &
$A_3$(null, one) : 0.0231 \\
$A_2$(forty, forty) : 0.0332 &
$A_2$(twenty, twenty) : 0.0310 \\
$A_2$(seventy, seventy) : 0.0296 &
$A_2$(sixty, sixty) : 0.0274 \\
$A_2$(ninety, ninety) : 0.0260 &
$A_3$(eighteen, nineteen) : 0.0064 \\
$A_3$(sixteen, seventeen) : 0.0049 &
$A_3$(eleven, twelve) : 0.0044 \\
$A_3$(nine, ten) : 0.0044 &
$A_3$(thirteen, fourteen) : 0.0044 \\
$A_3$(fourteen, fifteen) : 0.0039 &
$A_3$(ten, eleven) : 0.0034 \\
$A_2$(null, fifty) : 0.0043 &
$A_3$(eighty, null) : 0.0030 \\
$A_3$(seventeen, eighteen) : 0.0030 &
$A_3$(nine, sixty) : 0.0025 \\
$A_2$(nine, seventy) : 0.0029 &
$A_3$(nine, forty) : 0.0020 \\
$A_2$(null, thirty) : 0.0022 &
$A_2$(nine, ninety) : 0.0022 \\
$A_3$(twelve, thirteen) : 0.0015 &
$A_3$(fifteen, sixteen) : 0.0015 \\
$A_3$(null, comes) : 0.0010 &
$A_2$(twenty, after) : 0.0014 \\
$A_2$(sixty, before) : 0.0007 &
$A_3$(nineteen, comes) : 0.0005 \\
$A_4$(nine, thirty) : 0.0010 & \\
\end{tabular}
\caption{The grammar which produced Table \ref{tab:results}.}
\label{tab:grammar}
\end{table}
